Local Spectral Clustering of Density Upper Level Sets

### 2019-05-02 arxiv/arxiv_local_density_clustering.tex
proofs for cluster recovery section updated

\item In Section \ref{sec: consistent_cluster_estimation_with_ppr}, we show in
  Theorem \ref{thm: consistent_recovery_of_density_clusters} that these bounds
  in Theorems \ref{thm: conductance_upper_bound} and \ref{thm:
    inverse_mixing_time_lower_bound_nonconvex},
  on the cluster quality criteria, have algorithmic consequences for PPR:
  properly initialized, Algorithm \ref{alg: ppr} performs consistent density
  cluster estimation in the sense of \eqref{eqn:
    consistent_density_cluster_recovery}.

>>>>

\item In Section \ref{sec: consistent_cluster_estimation_with_ppr}, we show in
  Theorem \ref{thm: consistent_recovery_of_density_clusters} that the bounds
  in Theorems \ref{thm: conductance_upper_bound} and \ref{thm:
    inverse_mixing_time_lower_bound_nonconvex},
  on the cluster quality criteria, have algorithmic consequences for PPR:
  properly initialized, Algorithm \ref{alg: ppr} performs consistent density
  cluster estimation in the sense of \eqref{eqn:
    consistent_density_cluster_recovery}.

### 2019-05-02 arxiv/arxiv_local_density_clustering_proofs.tex
proofs for cluster recovery section updated

%%%%%%%% ICML 2019 submission %%%%%%%%%%%%%%%%%

@@

%%% Graph terms
\newcommand{\cut}{\mathrm{cut}}

@@

	There exists a good set $\Csig[\Xbf]^g \subseteq \Csig[\Xbf]$ with $\vol(\Csig[\Xbf]^g; G_{n,r}) \geq \vol(\Csig[\Xbf]; G_{n,r})/2$ such that the following statements hold with respect to $\pbf(v,\alpha;G_{n,r})$ for any $v \in \Csig[\Xbf]^g$:
	\begin{itemize}
		\item For each $u \in \Cset[\Xbf]$,
		\begin{equation}
		\label{eqn: lower_bound_PPR_in_cluster}
		\pbf(u) \geq \frac{4}{5} \widetilde{\pi}_{n,r}(u) - \frac{2 \Phi_{n,r}(\Csig[\Xbf])}{\Psi_{n,r}(\Csig[\Xbf]) \widetilde{D}_{\min}}
		\end{equation}
		\item For any $\Cset' \in \Cbb_f(\lambda)$ such that $\Cset' \neq \Cset$, and for each $u' \in \Csig'[\Xbf]$,
		\begin{equation}
		\label{eqn: upper_bound_PPR_in_other_cluster}
		\pbf(u') \leq \frac{2 \Phi_{n,r}(\Csig[\Xbf])}{\Psi_{n,r}(\Csig[\Xbf]) \widetilde{D}_{\min}}
		\end{equation}
	\end{itemize}
\end{lemma}

\begin{proof}
	The proof of Lemma \ref{lem: setup} is lengthy, but not difficult. We begin with some notation. Recall that $\Wbf_n = \Dbf_n \Abf_n^{-1}$ is the transition probability matrix over $G_{n,r}$. Let $\widetilde{\Dbf}_n$ and $\widetilde{\Wbf}_n$ be the degree and random walk matrices for the subgraph $\widetilde{G}_{n,r}$. Then, given $q \in \Reals^{\Csig[\Xbf]}$ we let
	\begin{equation}
	\widetilde{\pbf}_q = \alpha q + (1 - \alpha) \widetilde{\pbf}_{q} \widetilde{\Wbf}_n 
	\end{equation}
	be the \pprspace vector originating from $q$ over $\widetilde{G}_{n,r}$. (When the starting distribution $q = e_v$ is a point mass at a seed node $v \in \Csig[\Xbf]$, we write $\widetilde{\pbf}_v$ for $\widetilde{\pbf}_{e_v}$ in a slight abuse of notation).

	Our analysis will involve \emph{leakage} and \emph{soakage} vectors, defined by
	\begin{align*}
	\ell_t & := e_v (\Wbf_n \widetilde{\mathbf{I}}_n )^t (\mathbf{I}_n - \Dbf_n^{-1} \wDbf_{n}),~ \ell := \sum_{t = 0}^{\infty} (1 - \alpha)^t \ell_t, \\
	s_t & := e_v (\Wbf_n \widetilde{\mathbf{I}}_n )^t (\Wbf_n \widetilde{\mathbf{I}}_n^c),~ s := \sum_{t = 0}^{\infty} (1 - \alpha)^{t} s_t.
	\end{align*}
	where $\mathbf{I}_n$ is the $n \times n$ identity matrix, $\widetilde{\mathbf{I}}_n$ is an $n \times n$ diagonal matrix with $(\widetilde{\mathbf{I}}_n)_{uu} = 1$ if $u \in \Csig[\Xbf]$ and $0$ otherwise, and $\widetilde{\mathbf{I}}_n^c = \mathbf{I}_n - \widetilde{\mathbf{I}}_n$.

	In words, for $u \in \Csig[\Xbf]$, $\ell_t(u)$ is the probability that a random walk originating from $v$ stays within $\Csig[\Xbf]$ for $t$ steps, arriving at the $t$th step at $u$, and then leaks out of $\Csig[\Xbf]$ on the $t + 1$th step. For $w \not\in \Csig[\Xbf]$, $s_t(w) = 0$. By contrast, $s_t(w)$ is the probability that a random walk originating from $v$ stays within $\Csig[\Xbf]$ for $t$ steps, and then moves to $w$ on the $t + 1$ step, while $s_t(u) = 0$ for all $u \in \Csig[\Xbf]$. The vectors $\ell$ and $s$ then clearly have the same interpretation, but with respect to the total mass leaked and soaked by the \pprspace vector.

	We first prove \eqref{eqn: lower_bound_PPR_in_cluster}, and begin by restating some results of \citep{zhu2013}, adapted to our notation. By Lemma 3.1 of \citep{zhu2013}, there exists a good set $\Csig[\Xbf]^g \subseteq \Csig[\Xbf]$ with $\vol(\Csig[\Xbf]^g; G_{n,r}) \geq \vol(\Csig[\Xbf]; G_{n,r})/2$ such that for every $v \in \Csig[\Xbf]^g$
	\begin{equation}
	\label{eqn: zhulemma3.1}
	\pbf(u) \geq \widetilde{\pbf}_v(u) - \widetilde{\pbf}_{\ell}(u),~ \textrm{and}~ \norm{\ell}_1 \leq \frac{2 \Phi_{n,r}(\Csig[\Xbf])}{\alpha}.
	\end{equation}

	If moreover $\alpha \leq \frac{\Psi_{n,r}(\Csig[\Xbf])}{9}$, then additionally by Corollary 3.3 of \citep{zhu2013}, for every $u \in \Csig[\Xbf]$
	\begin{equation*}
	\widetilde{\pbf}(u) \geq \frac{4}{5} \widetilde{\pi}_{n,r}(u)
	\end{equation*}
	and along with \eqref{eqn: zhulemma3.1}, we obtain
	\begin{equation*}
	\pbf(u) \geq \frac{4}{5} \widetilde{\pi}_{n,r}(u) - \widetilde{\pbf}_{\ell}(u).
	\end{equation*}

	We proceed to upper bound $\widetilde{\pbf}_{\ell}(u) \leq \norm{\ell}_1 / \widetilde{D}_{\min}$, whence \eqref{eqn: lower_bound_PPR_in_cluster} follows by \eqref{eqn: zhulemma3.1}. We observe two facts regarding $\widetilde{\pbf}_{\ell}(u)$. First, for any $u \in \Cset$, since $r < \sigma$, $(u,w) \not\in G_{n,r}$ for any $w \not\in \Csig$. As a result, for all $t \geq 1$, $\ell_t(u) = 0$ and by extension, $\ell(u) = 0$ as well.

	Second, for any $q \in \Reals^{\Csig[\Xbf]}$ with $\sum_{w \in \Csig[\Xbf]} q(w) = 1$, and any $t \geq 1$,
	\begin{align*}
	q \widetilde{\Wbf}_n^t (u) & \leq \norm{q}_1 ||\widetilde{\Wbf}_{\cdot u}||_{\infty} \\
	& \leq \frac{1}{\widetilde{D}_{\min}}
	\end{align*}
	where $\widetilde{\Wbf}_{\cdot u}$ is the $u$th column of $\widetilde{\Wbf}$, and the last inequality follows from the fact $(u,w) \in \widetilde{G}_{n,r}$ implies $w \in \Csig$, and therefore
	\begin{equation*}
	\deg(w; \widetilde{G}_{n,r}) \geq \widetilde{D}_{\min}.
	\end{equation*}

@@

\end{proof}

\paragraph{Proof of Theorem \ref{thm: consistent_recovery_of_density_clusters}}

@@

		Lemma \ref{lem: sum_of_soakages} allows us to make the transition to sums of soakage vectors. 
		\begin{lemma}
			\label{lem: sum_of_soakages}

@@

	and as a result $\|s\|_1 = \|\ell\|_1$. Combining with $\|\ell\|_1 \leq 2 \frac{\widetilde{\Phi}_{n,r}}{\alpha}$ and (\ref{eqn: soakage_page_rank_body}) yields the desired upper bound.

\end{proof}

>>>>

%%%%%%%% Proofs of Local Spectral Clustering of Density Upper Level Sets %%%%%%%%%%%%%%%%%

@@

%%% Graph terms
\newcommand{\cut}{\mathrm{cut}}
\newcommand{\degminpr}{\deg_{\min}'}
\newcommand{\piminwt}{\widetilde{\pibf}_{\min}}

@@

	There exists a good set $\Csig[\Xbf]^g \subseteq \Csig[\Xbf]$ with $\vol(\Csig[\Xbf]^g; G_{n,r}) \geq \vol(\Csig[\Xbf]; G_{n,r})/2$ such that the following statements hold with respect to $\pbf(v,\alpha;G_{n,r})$ for any $v \in \Csig[\Xbf]^g$:
	\begin{itemize}
		\item For each $u \in \Cset[\Xbf]$,
		\begin{equation}
		\label{eqn: lower_bound_PPR_in_cluster}
		\pbf(u) \geq \frac{4}{5} \widetilde{\pi}_{n,r}(u) - \frac{2 \Phi_{n,r}(\Csig[\Xbf])}{\Psi_{n,r}(\Csig[\Xbf]) \widetilde{D}_{\min}}
		\end{equation}
		\item Let $\Cset' \neq \Cset \in \Cbb_f(\lambda)$ satisfy \ref{asmp: cluster_separation} with respect to $\Cset$. Then for each $u' \in \Csig'[\Xbf]$,
		\begin{equation}
		\label{eqn: upper_bound_PPR_in_other_cluster}
		\pbf(u') \leq \frac{2 \Phi_{n,r}(\Csig[\Xbf])}{\Psi_{n,r}(\Csig[\Xbf]) \degminpr}
		\end{equation}
		where $ \deg_{\min}' := \min_{u \in \Cset'[\Xbf]} \deg(u; G_{n,r})$. 
	\end{itemize}
\end{lemma}

\begin{proof}
	The proof of Lemma \ref{lem: setup} is lengthy, but not difficult. We begin with some notation. Recall that $\Wbf_n = \Dbf_n \Abf_n^{-1}$ is the transition probability matrix over $G_{n,r}$. Let $\widetilde{\Dbf}_n$ and $\widetilde{\Wbf}_n$ be the degree and random walk matrices for the subgraph $\widetilde{G}_{n,r}$. Then, given $q \in \Reals^{\Csig[\Xbf]}$ we let
	\begin{equation}
	\widetilde{\pbf}_q = \alpha q + (1 - \alpha) \widetilde{\pbf}_{q} \widetilde{\Wbf}_n 
	\end{equation}
	be the \pprspace vector originating from $q$ over $\widetilde{G}_{n,r}$. (When the starting distribution $q = e_v$ is a point mass at a seed node $v \in \Csig[\Xbf]$, we write $\widetilde{\pbf}_v := \widetilde{\pbf}_{e_v}$ in a slight abuse of notation).

	Our analysis will involve \emph{leakage} and \emph{soakage} vectors, defined by
	\begin{align}
	\label{eqn: leakage_soakage}
	\ell_t & := e_v (\Wbf_n \widetilde{\mathbf{I}}_n )^t (\mathbf{I}_n - \Dbf_n^{-1} \wDbf_{n}),~ \ell := \sum_{t = 0}^{\infty} (1 - \alpha)^t \ell_t, \nonumber \\
	s_t & := e_v (\Wbf_n \widetilde{\mathbf{I}}_n )^t (\Wbf_n \widetilde{\mathbf{I}}_n^c),~ s := \sum_{t = 0}^{\infty} (1 - \alpha)^{t} s_t.
	\end{align}
	where $\mathbf{I}_n$ is the $n \times n$ identity matrix, $\widetilde{\mathbf{I}}_n$ is an $n \times n$ diagonal matrix with $(\widetilde{\mathbf{I}}_n)_{uu} = 1$ if $u \in \Csig[\Xbf]$ and $0$ otherwise, and $\widetilde{\mathbf{I}}_n^c = \mathbf{I}_n - \widetilde{\mathbf{I}}_n$.

	In words, for $u \in \Csig[\Xbf]$, $\ell_t(u)$ is the probability that a random walk originating from $v$ stays within $\Csig[\Xbf]$ for $t$ steps, arriving at $u$ on the $t$th step, and then leaks out of $\Csig[\Xbf]$ on the $t + 1$th step. For $w \not\in \Csig[\Xbf]$, $s_t(w) = 0$. By contrast, $s_t(w)$ is the probability that a random walk originating from $v$ stays within $\Csig[\Xbf]$ for $t$ steps, and then moves to $w$ on the $t + 1$ step, while $s_t(u) = 0$ for all $u \in \Csig[\Xbf]$. The vectors $\ell$ and $s$ then give the total mass leaked and soaked, respectively, by the \pprspace vector.

	We first prove \eqref{eqn: lower_bound_PPR_in_cluster}, and begin by restating some results of \citep{zhu2013}, adapted to our notation. By Lemma 3.1 of \citep{zhu2013}, there exists a good set $\Csig[\Xbf]^g \subseteq \Csig[\Xbf]$ with $\vol(\Csig[\Xbf]^g; G_{n,r}) \geq \vol(\Csig[\Xbf]; G_{n,r})/2$ such that for every $v \in \Csig[\Xbf]^g$
	\begin{equation}
	\label{eqn: zhulemma3.1}
	\pbf(u) \geq \widetilde{\pbf}_v(u) - \widetilde{\pbf}_{\ell}(u),~ \textrm{and}~ \norm{\ell}_1 \leq \frac{2 \Phi_{n,r}(\Csig[\Xbf])}{\alpha}.
	\end{equation}
	(The result $\norm{\ell}_1 \leq \frac{2 \Phi_{n,r}(\Csig[\Xbf])}{\alpha}$ is the only result in the proof of Theorem \ref{thm: consistent_recovery_of_density_clusters} which relies on the restriction $v \in \Csig[\Xbf]^g$.)

	If additionally $\alpha \leq \frac{\Psi_{n,r}(\Csig[\Xbf])}{9}$, then by Corollary 3.3 of \citep{zhu2013}, for every $u \in \Csig[\Xbf]$
	\begin{equation*}
	\widetilde{\pbf}(u) \geq \frac{4}{5} \widetilde{\pi}_{n,r}(u)
	\end{equation*}
	and along with \eqref{eqn: zhulemma3.1}, we obtain
	\begin{equation*}
	\pbf(u) \geq \frac{4}{5} \widetilde{\pi}_{n,r}(u) - \widetilde{\pbf}_{\ell}(u).
	\end{equation*}

	We proceed to upper bound $\widetilde{\pbf}_{\ell}(u) \leq \norm{\ell}_1 / \widetilde{D}_{\min}$, whence \eqref{eqn: lower_bound_PPR_in_cluster} follows by \eqref{eqn: zhulemma3.1}. We observe two facts regarding $\widetilde{\pbf}_{\ell}(u)$. First, for any $u \in \Cset$, since $r < \sigma$, $(u,w) \not\in G_{n,r}$ for any $w \not\in \Csig$. As a result, for all $t \geq 1$, $\ell_t(u) = 0$ and by extension, $\ell(u) = 0$ as well. Second, for any $q \in \Reals^{\Csig[\Xbf]}$ with $\sum_{w \in \Csig[\Xbf]} q(w) = 1$, and any $t \geq 1$,
	\begin{align}
	\label{eqn: one_step_bound}
	q \widetilde{\Wbf}_n^t (u) & \leq \norm{q}_1 ||\widetilde{\Wbf}_{\cdot u}||_{\infty} \nonumber \\
	& \leq \frac{1}{\widetilde{D}_{\min}} 
	\end{align}
	where $\widetilde{\Wbf}_{\cdot u}$ is the $u$th column of $\widetilde{\Wbf}$, and the last inequality follows from the fact $(u,w) \in \widetilde{G}_{n,r}$ implies $w \in \Csig$, and therefore $\deg(w; \widetilde{G}_{n,r}) \geq \widetilde{D}_{\min}$.

@@

	We turn to showing \eqref{eqn: upper_bound_PPR_in_other_cluster}. By Lemma \ref{lem: soakage_ppr_lb}, for all $u' \not\in \Csig[\Xbf]$,
	\begin{equation*}
	\pbf_v(u') \leq \pbf_s(u').
	\end{equation*}

	Note that by \ref{asmp: cluster_separation}, for every $u \in \Csig[\Xbf], (u',u) \not\in E$ and therefore $s(u') = 0$. Some manipulations, similar to those in the preceding part of the proof, yield a lower bound on $\pbf_v(u')$ in terms of $\norm{s}_1$:
	\begin{align*}
	\pbf_s(u') & = \alpha \sum_{t = 0}^{\infty} (1 - \alpha)^t \left(s \Wbf_n^t\right)(u') \\
	& = \norm{s}_1 \alpha \sum_{t = 0}^{\infty} (1 - \alpha)^t \left(\frac{s}{\norm{s}_1} \Wbf_n^t\right)(u') \\
	& = \norm{s}_1 \alpha \sum_{t = 1}^{\infty} (1 - \alpha)^t \left(\frac{s}{\norm{s}_1} \Wbf_n^t\right)(u') \\
	& \leq \frac{\norm{s}_1}{\degminpr}
	\end{align*}
	where the last inequality follows from precisely the same reasoning as \eqref{eqn: one_step_bound}. The claim follows in light of Lemma \ref{lem: total_leakage_equal_total_soakage}, along with \eqref{eqn: zhulemma3.1}.
\end{proof}

We turn now to the proof of Theorem \ref{thm: consistent_recovery_of_density_clusters}. Let $\piminwt := \min_{u \in \Cset[\Xbf]} \widetilde{\pibf}_{n,r}(u)$.
\paragraph{Proof of Theorem \ref{thm: consistent_recovery_of_density_clusters}.}
~

Observe that the conditions of Theorem \ref{thm: consistent_recovery_of_density_clusters} subsume the requirement of Lemma \ref{lem: setup}, and therefore by that lemma we have the following bounds:
\begin{align*}
\pbf(u) & \geq \frac{4}{5} \widetilde{\pibf}_{n,r}(u) - \frac{2 \Phi_{n,r}(\Csig[\Xbf])}{\Psi_{n,r}(\Csig[\Xbf]) \widetilde{D}_{\min}} \tag{for each $u \in \Cset[\Xbf]$} \\
\pbf(u') & \leq \frac{2 \Phi_{n,r}(\Csig[\Xbf])}{\Psi_{n,r}(\Csig[\Xbf]) \degminpr} \tag{for each $u' \in \Cset'[\Xbf]$}
\end{align*}

We will further show that under the conditions of Theorem \ref{thm: consistent_recovery_of_density_clusters}, the following bound holds with probability tending to one as $n \to \infty$:
\begin{equation}
\label{eqn: gap_bounds}
\frac{\widetilde{\Phi}_{n,r}(\Csig[\Xbf])}{\Psi_{n,r}(\Csig[\Xbf]) \widetilde{D}_{\min}}, \frac{\widetilde{\Phi}_{n,r}(\Csig[\Xbf])}{\Psi_{n,r}(\Csig[\Xbf]) \degminpr} \leq \frac{1}{5} \piminwt,
\end{equation}
\textcolor{red}{which will prove the claim.}

By Lemma \ref{lem: ball_bounds_in_probability}, $\degminpr\cdot \widetilde{D}_{\min}$ is upper bounded,
\begin{equation}
\label{eqn: pimin_Dmin_lb}
\piminwt \cdot \widetilde{D}_{\min} = \frac{\widetilde{D}_{\min}^2}{\widetilde{\vol}_{n,r}(\widetilde{G}_{n,r})} \leq \frac{36}{625} \frac{\lambda^2 \nu_d r^d}{\Lambda_{\sigma} \nu_d \Pbb(\Csig)}  
\end{equation}
where the bound holds with probability tending to one as $n \to \infty$.

By Theorems \ref{thm: conductance_upper_bound} and \ref{thm: inverse_mixing_time_lower_bound}, with probability one as $n \to \infty$,
\begin{equation}
\label{eqn: difficulty_bound}
\frac{2\Phi_{n,r}(\Csig[\Xbf])}{\Psi_{n,r}(\Csig[\Xbf])} \leq \kappa_1(\Cset).
\end{equation}
\eqref{eqn: difficulty_bound}, \eqref{eqn: pimin_Dmin_lb} and \eqref{eqn: kappa2_ub} together show \eqref{eqn: gap_bounds}.

\subsection{Linear Algebra Facts}
\label{sec: linalg}

We state here a number of basic facts which follow from matrix manipulations. These will be used in the proof of Theorem \ref{thm: consistent_recovery_of_density_clusters}.

\begin{lemma}
	\label{lem: soakage_ppr_lb}
	For any $v \in \Csig[\Xbf]$ and $u \not\in \Csig[\Xbf]$,
	\begin{equation*}
	\pbf_{v}(u) \leq \pbf_{s}(u)
	\end{equation*}
	where $s$ is defined as in \eqref{eqn: leakage_soakage} and depends implicitly upon $v$.
\end{lemma}
\begin{proof}
	The statement follows from Lemma \ref{lem: sum_of_soakages} along with a series of algebraic manipulations,
	\begin{align*}
	\pbf_v(u) & = \alpha\sum_{T = 0}^{\infty} (1 - \alpha)^t \left(e_v \Wbf_n^T\right)(u) \\
	& = \alpha\sum_{T = 1}^{\infty} (1 - \alpha)^t \left(e_v \Wbf_n^T\right)(u) \\
	& \leq \alpha \sum_{T=1}^{\infty} (1 - \alpha)^T \left( \sum_{t = 0}^{T - 1} s_t \Wbf_n^{T - t - 1} \right)(u) \tag{Lemma \ref{lem: sum_of_soakages}}\\
	& = \alpha \sum_{t=0}^{\infty} \sum_{T = t + 1}^{\infty} (1 - \alpha)^T \left( s_t \Wbf_n^{T - t - 1} \right)(u)\\
	& = \alpha \sum_{t=0}^{\infty} \sum_{\Delta = 0}^{\infty} (1 - \alpha)^{\Delta + t + 1} \left( s_t \Wbf_n^{\Delta} \right)(u) \\
	& \leq \alpha \sum_{t=0}^{\infty} \sum_{\Delta = 0}^{\infty} (1 - \alpha)^{\Delta + t } \left( s_t \Wbf_n^{\Delta} \right)(u) \\
	& = \alpha \sum_{\Delta = 0}^{\infty} (1 - \alpha)^{\Delta} \left(s \Wbf_n^{\Delta}\right)(u) \\
	& = \pbf_s(u)
	\end{align*}
\end{proof}

Let $s_t := q(\Wbf \Ibf{S})^t(\Wbf(\Ibf{S^c}))$ be the soakage vector out of $S \subseteq V$, where $\Ibf{S}$ is a $\abs{V} \times \abs{V}$ diagonal matrix with $(\Ibf{S})_{uu} = 1$ if $u \in S$ and 0 otherwise, and $\Ibf{S^c} := \Ibf{} - \Ibf{S}$. 
\begin{lemma}
	\label{lem: sum_of_soakages}
	Let $G = (V,E)$ be an unweighted, undirected graph with associated random walk matrix $\Wbf$. For any $T \in \mathbb{N}, T \geq 1$, $q \in \Reals^{\abs{V}}$, and $S \subseteq V$
	\begin{equation}
	\label{eqn: sum_of_soakages}
	q\Wbf^T = \sum_{t = 0}^{T - 1} s_t \Wbf^{T - t - 1} + q(\Wbf \Ibf{S})^T
	\end{equation}
	In particular, if $u \in V\setminus S$, then
	\begin{equation}
	\label{eqn: sum_of_soakages_2}
	q\Wbf^T(u) = \sum_{t = 0}^{T - 1} \left(s_t \Wbf^{T - t - 1}\right)(u)
	\end{equation}
\end{lemma}
\begin{proof}	
	We show \eqref{eqn: sum_of_soakages}, from which \eqref{eqn: sum_of_soakages_2} is an immediate consequence.

	To show \eqref{eqn: sum_of_soakages}, we proceed by induction on $T$. When $T = 1$,
	\begin{equation*}
	q\Wbf = q\Wbf\Ibf{S} + q\Wbf\Ibf{S^c} =  q\Wbf\Ibf{S} + s_0. 
	\end{equation*}

	Then, for $T \in \mathbb{N},~ T \geq 2$,
	\begin{align*}
	q\Wbf^{T} & = q\Wbf^{T - 1}{\Wbf} \\
	& = \left\{\sum_{t = 0}^{T - 2} s_t \Wbf^{T - 2 - t} + q(\Wbf \Ibf{S})^{T - 1} \right\} \Wbf \tag{by the inductive hypothesis}\\
	& = \sum_{t = 0}^{T - 2} s_t \Wbf^{T - 1 - t} + q(\Wbf \Ibf{S})^{T - 1} (\Wbf \Ibf{S} + \Wbf \Ibf{S^c}) \\
	& = \sum_{t = 0}^{T - 1} s_t \Wbf^{T - 1 - t} + q(\Wbf \Ibf{S})^{T - 1} (\Wbf \Ibf{S})
	\end{align*}
	and the proof is complete.
\end{proof}

\begin{lemma}
	\label{lem: total_leakage_equal_total_soakage}
	Letting $s_t$, $\ell_t$ $s$ and $\ell$ be as in \eqref{eqn: leakage_soakage},
	\begin{equation*}
	\norm{s_t}_1 = \norm{\ell_t}_1,~ \textrm{for each $t \geq 0$}
	\end{equation*}
	and therefore $\norm{s}_1 = \norm{\ell}_1$. 
\end{lemma}
\begin{proof}
	By the definition of $s_t$ and $\ell_t$, we have
	\begin{align*}
	\norm{s_t}_1 & = \norm{q_t (\Wbf_n \widetilde{\mathbf{I}}_n^c)}_1 \\
	& = \sum_{u \in \Xbf} \sum_{u' \in \Xbf} q_t(u) (\Wbf_n \widetilde{\mathbf{I}}_n^c)(u, u') \\
	& = \sum_{u \in\Csig[\Xbf]} \sum_{u' \in \Csig[\Xbf]^c} \frac{q_t(u)}{(\Dbf_n)_{uu}} \1((u,u') \in G_{n,r}) \\
	& = \sum_{u \in \Csig[\Xbf]} \frac{q_t(u) \left((\Dbf_n)_{uu} - (\widetilde{\Dbf}_n)_{uu} \right)}{(\Dbf_n)_{uu}} \\
	& = \norm{q_t (\Ibf{n} - \Dbf_n^{-1} \widetilde{\Dbf}_n)}_1 = \norm{\ell_t}_1.
	\end{align*}
\end{proof}

@@

		Lemma \ref{lem: sum_of_soakages} allows us to make the transition to sums of soakage vectors. 
		\begin{lemma}

@@

	and as a result $\|s\|_1 = \|\ell\|_1$. Combining with $\|\ell\|_1 \leq 2 \frac{\widetilde{\Phi}_{n,r}}{\alpha}$ and (\ref{eqn: soakage_page_rank_body}) yields the desired upper bound.
\end{proof}

\paragraph{Proof of Theorem \ref{thm: consistent_recovery_of_density_clusters}.}
